### 2021-02-15 paper.tex
Parts of introduction and future work.

%===========[ PREAMBLE ]========================================================
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper, top=0.98in, bottom=0.79in, left=0.98in, right=0.98in]{geometry}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[labelsep=period]{caption}
\usepackage{mwe}
\usepackage{xfrac}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
%\usepackage[backend=biber, style=ieee]{biblatex} %For bibliography management with biblatex
%\addbibresource{/path/to/bib/file/example.bib} %Change path to your own .bib file

@@

%===========[ TITLES ]==========================================================
%Chnage to your own information
\newcommand{\contribtitle}{Contribution title}
\newcommand{\contribsubtitle}{Subtitle}
\newcommand{\firstauthor}{First Author\textsuperscript{1[https://orcid.org/0000-1111-2222-3333]}}
\newcommand{\firstauthoruniv}{University College London, UK}
\newcommand{\secondauthor}{Second Author\textsuperscript{2[https://orcid.org/1111-2222-3333-4444]}}
\newcommand{\secondauthoruniv}{TIB Open Publishing, Germany}
\newcommand{\thirdauthor}{Third Author\textsuperscript{3[https://orcid.org/1111-2222-3333-4444]}}
\newcommand{\thirdauthoruniv}{Technische Hochschule Wildau, Germany}

@@

\paragraph{Abstract.} The abstract should summarize the contents of the paper in short terms, i.e. in up to 250 words.
\paragraph{Keywords:} First keyword, second, third keyword

\section*{First Section}
\subsection*{Subsection} Please notice that there is no indent in the first paragraph of a section or subsection. There is also no indent in the first paragraphs which follow a table, figure, equation, etc. \par

Nevertheless, following paragraphs are indented.

@@

@@

\begin{enumerate}
    \item J. K. Author, “Name of paper,” Abbrev. Title of Journal , vol.x, no.x, pp. xxx–xxx, Abbrev. month, year, doi: https.doi.org/……
    \item J. K. Author, “Title of chapter in the book,” in Title of Their Published Book, xth ed. City of Publisher, (only U.S. State), Country: Abbrev. of Publisher, year, ch. x, sec. x, pp. xxx–xxx.
    \item First Name Initial(s) Last Name. “Page Title.” Website Title. Web Address (retrieved Date Accessed)
\end{enumerate}

%\printbibliography[heading=none] %Uncomment if using biblatex. This command generates the refrences section automatically.

\noindent NOTE: You can create your technical contribution directly in this template. Make a copy of it beforehand for safety. This template was compiled using the pdflatex compiler. Using another compiler might result in a different format. For a more optimal bibliography management, consider using tools such as \href{https://www.overleaf.com/learn/latex/bibliography_management_with_bibtex}{BibTeX} or \href{https://www.overleaf.com/learn/latex/bibliography_management_with_biblatex}{Biblatex}.
\end{document}

>>>>

%===========[ PREAMBLE ]========================================================
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper, top=0.98in, bottom=0.79in, left=0.98in, right=0.98in]{geometry}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{csquotes}
\usepackage[labelsep=period]{caption}
\usepackage{mwe}
\usepackage{xfrac}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{cleveref}
%\usepackage[backend=biber, style=ieee]{biblatex} %For bibliography management with biblatex
%\addbibresource{/path/to/bib/file/example.bib} %Change path to your own .bib file

@@

%===========[ TITLES ]==========================================================
%Chnage to your own information
%\newcommand{\contribtitle}{FAIR Knowledge Graphs for the Management of Health Information Systems}
\newcommand{\contribtitle}{SNIK Graph}
\newcommand{\contribsubtitle}{Graph-Based RDF Exploration}
%\newcommand{\contribsubtitle}{Graph-Based Exploration of an Hospital Information Systems}
\newcommand{\firstauthor}{Konrad Höffner\textsuperscript{1[https://orcid.org/0000-0001-7358-3217]}}
\newcommand{\firstauthoruniv}{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Germany}
\newcommand{\secondauthor}{Second Author\textsuperscript{2[https://orcid.org/1111-2222-3333-4444]}}
\newcommand{\secondauthoruniv}{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Germany}
\newcommand{\thirdauthor}{Third Author\textsuperscript{3[https://orcid.org/1111-2222-3333-4444]}}
\newcommand{\thirdauthoruniv}{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Germany}

@@

\paragraph{Abstract.}% The abstract should summarize the contents of the paper in short terms, i.e. in up to 250 words.

\paragraph{Keywords:} Linked open data, health information systems, information management

\section*{Introduction}%
SNIK Graph is a web application\footnote{\url{http://www.snik.eu/graph}} that visualizes RDF resources as nodes and triples as edges of a graph.
The graph is visualized using the Cytoscape.js~\cite{cytoscape} library with the force-directed Euler layout. %, see%~\cref{fig:snik-graph-overview}.
With several thousand classes, specific parts of SNIK can be hard to discern.
Thus, there are several options to view subgraphs of SNIK, for example to show only a specific chapter of a book to prepare a lecture about a specific topic.
Users can also search for and restrict the view to a single class and then show the neighbourhood of that class %(see \cref{fig:snik-graph-circle-star})
 and subsequently the neighbourhood of selected neighbours of the previous step.
SNIK Graph can also calculate the shortest path to between classes.
Path and neighourhood operations are joined in the \enquote{spider worm}
%(see \cref{fig:snik-graph-spiderworm})
, which consists of the shortest path between a start node and an end node together with the end node’s neighbourhood, illustrate the context of a concept.

\subsection*{Motivation}%
- best presentation form depends on 
-

@@

\section*{Future Work}
\subsection*{Performance}
%On graphs of several thousand nodes, 
The performance of SNIK Graph suffers in two key areas:

%(1) Performing a force directed 
\subsubsection*{Force-Directed Layouts}
As CPUs with 6 to 16 cores become the norm, the speed penalty of single-threaded code becomes enormous.
Thus, the single-thread paradigm of JavaScript seriously hinders performance of CPU-bound applications like SNIK Graph.
While web workers\footnote{\url{https://html.spec.whatwg.org/multipage/workers.html\#workers}} offer multithreading for JavaScript applications, they posess separate memory and cause large overheads for serialization and deserialization and are thus not suited for short-lived tasks like calculating a single step of a force-directed layout for parts of a given graph.
Thus, a light-weight parallellization option is needed.
The WebAssembly \enquote{threads}-proposal\footnote{\url{https://github.com/WebAssembly/proposals/issues/14}} provides such a construct, however it is only at phase 2 \enquote{Proposed Spec Text Available}, which need to be followed by the implementation and the standardization phase.
The main developer of the Cytoscape.js library showed interest in rewriting a future version of the library in WebAssembly.

\subsubsection*{Graph Rendering}
Due to the low performance of rendering on an HTML canvas, the frame rate drops significantly below a fluent 60 frames per second.
The frame rate is especially low on large resoultions such as 4k (3840x2160) and on browsers other than Google Chrome (see table ...), where it can get as low as 2 FPS.
%Another ... incredible power of modern GPUs.

\subsubsection*{Most Interesting Path}
- We also tried to automatically find the most interesting path but this was not successfull as it is subjective and the depends on the goal of the user.
(link to AB bachelor thesis if allowed)

@@

%\printbibliography[heading=none] %Uncomment if using biblatex. This command generates the refrences section automatically.
\bibliographystyle{plain}
\bibliography{paper,snik}

\end{document}
